---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# labelspreserve

Whenever we perform some manipulations on a tibble with some variable labels, we tend to lose those attributes. Some times it may be pain to re-write the variables again. This package answers that question by preserving the variable labels before you perform such actions then you can restore those labels. 

## Installation

You can install the released version of labelspreserve like so:
``` r
devtools::install_github("mosesotieno/labelspreserve")
```


## Quick demo

Preserving and restoring variables with `labelspreserve`

```{r example}
library(labelspreserve)

# Load a dataset with variable labels

trial <- gtsummary::trial

# We first begin by preserving the variables 

preservelabels(trial)

# Computations and manipulations
# Example: Drop the label for trt  


attr(trial[["trt"]], "label") <- NULL
str(trial)


# Restore back the labels

trial <- restorelabels(trial, data_labels)
str(trial)


# Voila!
```

